\documentclass[11pt,a4paper]{article}

\usepackage[left=0.7in,right=0.7in,top=0.7in,bottom=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
}

\pagenumbering{gobble}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{Your Name}} \\
    \vspace{4pt}
    Platform Engineer \\
    \vspace{4pt}
    Email: your.email@example.com \quad
    GitHub: \href{https://github.com/yourusername}{github.com/yourusername} \quad
    LinkedIn: \href{https://linkedin.com/in/yourusername}{linkedin.com/in/yourusername}
\end{center}

\vspace{8pt}

\section*{Professional Summary}

Platform Engineer with 3+ years of experience building and operating scalable internal platforms that enable engineering teams to ship faster and more reliably. Specialized in designing cloud-native backend services using \textbf{Django} and \textbf{FastAPI}, with a strong emphasis on resilience, observability, and operational excellence.

Deep hands-on experience in infrastructure automation and GitOps, leveraging \textbf{Terraform}, \textbf{Ansible}, and \textbf{Kubernetes} with \textbf{Argo CD} and \textbf{Flux}. Proven ability to build self-service platforms, standardized deployment workflows, and secure multi-tenant systems that improve developer productivity and reduce cognitive load.

Experienced in building platform tooling and Kubernetes extensions in \textbf{Go}, including custom CLIs and controllers. Also developing AI-enabled internal developer tools using \textbf{LangChain} and \textbf{LangGraph} to power intelligent workflows and automation.

\vspace{6pt}

\section*{Technical Skills}

\textbf{Programming:} Go, Python, Bash \\
\textbf{Backend Frameworks:} Django, FastAPI \\
\textbf{Infrastructure as Code:} Terraform, Ansible \\
\textbf{Containerization \& Orchestration:} Docker, Kubernetes \\
\textbf{GitOps:} Argo CD, Flux \\
\textbf{Cloud Platforms:} AWS / GCP / Azure (adjust as applicable) \\
\textbf{Observability:} Prometheus, Grafana, ELK Stack, OpenTelemetry \\
\textbf{CI/CD:} GitHub Actions, GitLab CI, Jenkins (adjust as applicable) \\
\textbf{AI Tooling:} LangChain, LangGraph

\vspace{6pt}

\section*{Professional Experience}

\textbf{Platform Engineer} \hfill Company Name \\
\textit{Location \quad | \quad Start Date -- Present}

\begin{itemize}[leftmargin=*, itemsep=4pt]
    \item Designed and operated scalable internal platform services enabling engineering teams to deploy and manage workloads reliably.
    \item Built cloud-native backend services using Django and FastAPI with strong focus on fault tolerance, performance, and security.
    \item Implemented GitOps workflows using Argo CD and Flux to standardize deployments across multiple Kubernetes clusters.
    \item Automated infrastructure provisioning with Terraform and configuration management with Ansible.
    \item Designed and maintained multi-tenant Kubernetes environments with RBAC, network policies, and security best practices.
    \item Built internal platform tooling and Kubernetes controllers in Go to abstract infrastructure complexity and enforce platform standards.
    \item Developed self-service deployment pipelines and golden paths to improve developer velocity and reduce operational overhead.
    \item Integrated observability stacks (Prometheus, Grafana, logging systems) to improve system visibility and incident response.
    \item Built AI-enabled internal tooling using LangChain and LangGraph to automate workflows and enhance developer experience.
\end{itemize}

\vspace{6pt}

\section*{Key Projects}

\textbf{Internal Developer Platform (IDP)} \\
\begin{itemize}[leftmargin=*, itemsep=4pt]
    \item Designed a self-service platform enabling teams to provision services and deploy applications via standardized templates.
    \item Reduced deployment lead time and improved reliability through GitOps-driven workflows.
\end{itemize}

\textbf{Kubernetes Automation Toolkit (Go-based CLI \& Controllers)} \\
\begin{itemize}[leftmargin=*, itemsep=4pt]
    \item Developed custom Kubernetes controllers and CLI tools in Go to enforce policy, validate configurations, and streamline onboarding.
    \item Abstracted infrastructure complexity and reduced platform support overhead.
\end{itemize}

\textbf{AI-Enabled Workflow Automation} \\
\begin{itemize}[leftmargin=*, itemsep=4pt]
    \item Integrated LangChain and LangGraph into internal systems to automate operational tasks and provide intelligent developer assistance.
\end{itemize}

\vspace{6pt}

\section*{Education}

\textbf{Bachelor’s Degree in Computer Science (or relevant field)} \\
University Name \hfill Graduation Year

\vspace{6pt}

\section*{Additional Information}

\begin{itemize}[leftmargin=*, itemsep=4pt]
    \item Strong focus on platform reliability, clear abstractions, and fast feedback loops.
    \item Thrive in ownership-driven environments with high engineering standards.
\end{itemize}

\end{document}
